Context Specification

### 2025-05-13 nbs/development/context.qmd
docs(development): update context title
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: "Scientific Context Specification"
format:
  html:
    mermaid-format: js
    mermaid:
      theme: dark
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
---

>>>>

---
title: "Context Specification"
format:
  html:
    mermaid-format: js
    mermaid:
      theme: dark
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
---
